---
title: "Psych 250b equations"
author: "Lillian King"
date: "2026-04-07"
output: word_document
---

#F-statistic oneway
for ch3 q19 (or q1d in the hw)
```{r}
n1<- 38
n2<- 39
n3<- 39
n4<- 39
tot_mu<- 3.35
mu1<- 3.4
mu2<- 3.7
mu3<- 3.5
mu4<- 2.8
df_between<- 3
ss_between<-n1*((mu1-tot_mu)^2)+n2*((mu2-tot_mu)^2)+n3*((mu3-tot_mu)^2)+n4*((mu4-tot_mu)^2)
ms_between<-ss_between/df_between
ms_within<-2.152 
ms_between/ms_within #this is the f stat
```

#f stat for contrasts
this chunk and the CI chunk below are for ch4 q3 (or hw ch2a)
```{r}
n1<- 6
n2<- 6
n3<- 6

mu1<- 53.66
mu2<- 52.16
mu3<- 63.33

c1<- 1
c2<- (-1)
c3<- (0)

psi<-(c1*mu1)+(c2*mu2)+(c3*mu3)
sum_cn<-((c1^2)/n1)+((c2^2)/n2)+((c3^2)/n3)
ms_within<- 55.03

f_stat<-(psi^2)/(sum_cn*ms_within)
f_stat
```

#CI for f stat w contrast
this is the 2nd part of the above code, so its vars are almost all set in the chunk above
```{r}
f_crit<-4.21 #i got this by looking up a table of f-stat critical values
hi<-(psi)+(sqrt(f_crit)*sqrt(ms_within*sum_cn))
lo<-(psi)-(sqrt(f_crit)*sqrt(ms_within*sum_cn))
hi
lo
```

#Observed Value for bonfironni
this might be wrong, but its what the book says to do on pg. 227
```{r}
alpha_PC<- 0.05/3 #this is alpha/number of comparisons
df1<-2 #this is a-1 or num of groups -1
df2<-15 #this is N-a or num of ppl - num of groups
qf((1-alpha_PC), df1, df2)
```



#HW 2
#bonfironi Critical Value
```{r}
bon_f<-
bcv<-sqrt(bon_f)
bcv
```


#scheffe Critical Value
```{r}
schef_f<-
a<-
scv<-(a-1)*(schef_f)
scv
```


#Tukey Critical Value
```{r}
tuk_q<-
tcv<-(tuk_q^2)/2
tcv
```





