---
title: "Psych 250b equations"
author: "Lillian King"
date: "2026-04-07"
output: word_document
---

#F-statistic oneway
for ch3 q19 (or q1d in the hw)
```{r}
n1<- 38
n2<- 39
n3<- 39
n4<- 39
tot_mu<- 3.35
mu1<- 3.4
mu2<- 3.7
mu3<- 3.5
mu4<- 2.8
df_between<- 4
ss_between<-n1*((mu1-tot_mu)^2)+n2*((mu2-tot_mu)^2)+n3*((mu3-tot_mu)^2)+n4*((mu4-tot_mu)^2)
ms_between<-ss_between/df_between
ms_within<-2.152 
ms_between/ms_within #this is the f stat
```

#f stat for contrasts (bonferoni?)
this chunk and the CI chunk below are for ch4 q3 (or hw ch2a)
```{r}
n1<- 15
n2<- 15
n3<- 15
n4<- 15
n5<- 15

mu1<- 80
mu2<- 83
mu3<- 87
mu4<- 89
mu5<- 91

c1<- (-2)
c2<- (-1)
c3<- (0)
c4<- (-1)
c5<- (2)

psi<-(c1*mu1)+(c2*mu2)+(c3*mu3)+(c4*mu4)+(c5*mu5)
sum_cn<-((c1^2)/n1)+((c2^2)/n2)+((c3^2)/n3)
ms_within<- 55.03

f_stat<-(psi^2)/(sum_cn*ms_within)
f_stat
```

#CI for f stat w contrast
this is the 2nd part of the above code, so its vars are almost all set in the chunk above
```{r}
f_crit<-4.21 #i got this by looking up a table of f-stat critical values
hi<-(psi)+(sqrt(f_crit)*sqrt(ms_within*sum_cn))
lo<-(psi)-(sqrt(f_crit)*sqrt(ms_within*sum_cn))
hi
lo
```

#Observed Value for bonfironni
this might be wrong, but its what the book says to do on pg. 227
OK i dont think this is how to get the bonferoni observed value, but i do think its how to get the bonferoni critical value? like the same as the table? maybe? im not totally sure still tbh...
```{r}
alpha_PC<- 0.05/1 #this is alpha/number of comparisons
df1<-1 #this is a-1 or num of groups -1
df2<-75 #this is N-a or num of ppl - num of groups
qf((1-alpha_PC), df1, df2)
```



#HW 2
#df calculations
```{r}
K<-5#number of groups
N<-75#total number of ppl across all groups
schef_df_denom<-(K-1)
schef_df_numarat<-(N-K)
bon_df_denom<-(1)
bon_df_numarat<-(N-K)
tukey_df_denom<-(K)
tukey_df_numarat<-(N-K)
```


#bonfironi Critical Value
so table 3 in the doc of cv's michael gave us has the bon corrected CV, but the equ below will let you calc the bon corrected cv from the notmal table of CVs (table 2)
```{r}
bon_f<-4.54
bcv<-sqrt(bon_f)
bcv
```


#scheffe Critical Value
michael didnt give us the scheffe corected cv table, so we have to calc it from the normal table (tabel 2)
```{r}
schef_f<- 2.53
a<- 5
scv<-(a-1)*(schef_f)
scv
```


#Tukey Critical Value
use table 4?
```{r}
tuk_q<-3.67
tcv<-(tuk_q^2)/2
tcv
```


#HW 3
#f stat for contrasts (linear?)
this chunk and the CI chunk below are for ch6 q6
```{r}
n_group<- 15 #number of ppl in one group
n_tot<-75 #number of ppl in total

mu1<- 80
mu2<- 83
mu3<- 87
mu4<- 89
mu5<- 91

c1<- (-2)
c2<- (-1)
c3<- (0)
c4<- (1)
c5<- (2)

psi_lin<-(c1*mu1)+(c2*mu2)+(c3*mu3)+(c4*mu4)+(c5*mu5)
sum_c<- 10
ss_lin<-((psi_lin^2)*n_group)/sum_c
ms_within<- 150

f_stat<-(ss_lin)/(ms_within)
f_stat
```

#F-statistic omnibus
for ch6 q6
```{r}
n_group<- 15 #number of ppl in one group
n_tot<-75 #number of ppl in total

mu1<- 80
mu2<- 83
mu3<- 87
mu4<- 89
mu5<- 91

tot_mu<- 86

df_between<- 4
ss_between<-n_group*(((mu1-tot_mu)^2)+((mu2-tot_mu)^2)+((mu3-tot_mu)^2)+((mu4-tot_mu)^2)+((mu5-tot_mu)^2))
ms_between<-ss_between/df_between
ms_within<-150
ms_between/ms_within #this is the f stat
```

#HW 4

#Q1a
```{r}
a_rows<- 3
b_levels<- 2
ab<-b_levels*a_rows
df_win<- 60
N<-ab+df_win
n_group<-N/ab
tot_mu<- 10
mu1<- 12
mu2<- 10
mu3<- 8
ss_A<-(n_group*a_rows)*(((mu1-tot_mu)^2)+((mu2-tot_mu)^2)+((mu3-tot_mu)^2))
ss_A
```

#Q1b
```{r}
ss_B<-(n_group*b_levels)*(((mu1-tot_mu)^2)+((mu2-tot_mu)^2)+((mu3-tot_mu)^2))
ss_B
```

#Q1c
```{r}
df_win<-N-(a_rows*b_levels)
df_win
df_a<-(a_rows-1)
df_a
df_b<-(b_levels-1)
df_b
df_ab<-(a_rows-1)
df_ab
```


#Q1d
```{r}
ms_A<-ss_B/df_a
ms_A
ms_B<-ss_A/df_b
ms_B
AxB<-44
ms_AB<-AxB/df_ab
ms_AB
ss_win<-1620
ms_win<-ss_win/df_win
ms_win
```

#Q1e
```{r}
F_A<-ms_A/ms_win
F_A
F_B<-ms_B/ms_win
F_B
F_AB<-ms_AB/ms_win
F_AB
```

```{r}
ss_tot<-2104
```

